### 2024-11-20 paper/overview.tex
Add code font for tilde and dollar
Write overview

\begin{figure}[h]
  \centerline{\includegraphics[width=15cm]{fig/overview}}
  \caption[An overview of the SpecTec architecture]
    {An overview of the SpecTec architecture}
    \label{fig:overview}
\end{figure}

We propose SpecTec ...

% Overview explanation
In this chapter, we explain an overall approach to generate multiple artifacts
from the specification and check correctness of the specification.
\cref{fig:overview} illustrates the overview of our approach.
SpecTec provides a domain specific language (DSL) for the specification.
It is designed to be similar to the formal notation when describing the
semantics with compact and user-friendly notation.
It is type checked to prevent meta-level errors such as notation misuses and
dimension mismatches.
The code below is the specification for \texttt{testop} instruction written in
the DSL.
\begin{lstlisting}
  rule Step_pure/testop:
  (CONST nt c_1) (TESTOP nt testop)  ~>  (CONST I32 c)
  -- if c = $testop_(nt, testop, c_1)
\end{lstlisting}

>>>>

\begin{figure}[t]
  \centerline{\includegraphics[width=15cm]{fig/overview}}
  \caption[An overview of the SpecTec architecture]
    {An overview of the SpecTec architecture}
    \label{fig:overview}
\end{figure}

% Overview explanation
In this chapter, we explain the overall approach to generating multiple
artifacts from the specification and ensuring the correctness of the
specification. \Cref{fig:overview} illustrates an overview of our approach.
% DSL
SpecTec provides a domain-specific language (DSL) for writing specifications.
It is a declarative language designed to resemble the formal notation while
offering a compact and user-friendly syntax.
The code below shows the specification for the \texttt{testop} instruction
written in the DSL:
\begin{lstlisting}[escapechar=\%]
  rule Step_pure/testop:
  (CONST nt c_1) (TESTOP nt testop)  %$\tildecode$%>  (CONST I32 c)
  -- if c = %$\dollarcode$%testop_(nt, testop, c_1)
\end{lstlisting}
The DSL is type checked to prevent meta-level errors such as notation misuses and
dimension mismatches.
Using the DSL, SpecTec generates LaTeX code and mechanized definitions for theorem provers.

% AL
Additionally, SpecTec introduces another imperative language, \textit{AL}, for
the prose notation.
In AL, semantics are expressed algorithmically, in the form of step-by-step
instructions that take inputs and perform operations, mirroring the prose notation.
SpecTec translates declarative definitions in the DSL into algorithmic
definitions in AL.
The AL code below is the specification for the \texttt{testop} instruction
generated from the DSL:
\begin{lstlisting}[escapechar=\%]
Step_pure/testop nt testop {
 Assert (top_value(nt))
 Pop (numtype_0.CONST c_1)
 Let c = %$\dollarcode$%testop_(nt, testop, c_1)
 Push (I32.CONST c)
}
\end{lstlisting}
Using AL, SpecTec generates reStructuredText code.
\cref{fig:spectec-testop} shows the generated document for \texttt{testop}
instruction.
The generated document closely resembles the official document except for some
minor notation changes and some missing hyperlinks.

% AL interpreter
A notable feature of AL is that it is interpretable.
SpecTec includes an AL interpreter that executes an AL program with given inputs
and produces results.
Since an AL program specify the behavior of a Wasm program, the input to an AL
program is a Wasm program, and the result is the execution outcome of the Wasm
program.
In other words, the generated AL program functions as a WebAssembly interpreter.
What is particularly intriguing is that if specification authors write a Wasm
specification using the DSL, a WebAssembly interpreter that adheres to the
defined semantics is automatically generated.
By testing this generated interpreter, we can assess the specification,
thereby ensuring its correctness.
